---
title: "Supervised Learning in R: Regression"
output: html_notebook
---

### Multivariate linear regression (Part 1)

```{r}
# Load data
bloodpressure <- readRDS("data/bloodpressure.rds")
summary(bloodpressure)

# Create the formula and print it
fmla <- blood_pressure ~ age + weight
fmla

# Fit the model: bloodpressure_model
bloodpressure_model <- lm(fmla, bloodpressure)

# Print bloodpressure_model and call summary() 
bloodpressure_model
summary(bloodpressure_model)
```

One of the advantages of linear regression is that you can interpret the effects of each variable on the input – to a certain extent. In this case the coefficients for both age and weight are positive, which indicates that bloodpressure tends to increase as both age and weight increase.

### Multivariate linear regression (Part 2)

```{r}
library(ggplot2)

# Predict blood pressure using bloodpressure_model :prediction
bloodpressure$prediction <- predict(bloodpressure_model)

# Plot the results
ggplot(bloodpressure, aes(x = prediction, y = blood_pressure)) + 
    geom_point() +
    geom_abline(color = "blue")
```

The results stay fairly close to the line of perfect prediction, indicating that the model fits the training data well. From a prediction perspective, multivariate linear regression behaves much as simple (one-variable) linear regression does.
