---
title: "Supervised Learning in R: Regression"
output: html_notebook
---

### Multivariate linear regression (Part 1)

```{r}
# Load data
bloodpressure <- readRDS("data/bloodpressure.rds")
summary(bloodpressure)

# Create the formula and print it
fmla <- blood_pressure ~ age + weight
fmla

# Fit the model: bloodpressure_model
bloodpressure_model <- lm(fmla, bloodpressure)

# Print bloodpressure_model and call summary() 
bloodpressure_model
summary(bloodpressure_model)
```

One of the advantages of linear regression is that you can interpret the effects of each variable on the input – to a certain extent. In this case the coefficients for both age and weight are positive, which indicates that bloodpressure tends to increase as both age and weight increase.

### Multivariate linear regression (Part 2)

```{r}
library(ggplot2)

# Predict blood pressure using bloodpressure_model :prediction
bloodpressure$prediction <- predict(bloodpressure_model)

# Plot the results
ggplot(bloodpressure, aes(x = prediction, y = blood_pressure)) + 
    geom_point() +
    geom_abline(color = "blue")
```

The results stay fairly close to the line of perfect prediction, indicating that the model fits the training data well. From a prediction perspective, multivariate linear regression behaves much as simple (one-variable) linear regression does.

## Training and Evaluating Regression Models

### Graphically evaluate the unemployment model

In this exercise you will graphically evaluate the unemployment model, `unemployment_model`, that you fit to the unemployment data in the previous chapter. Recall that the model predicts `female_unemployment` from `male_unemployment`.

You will plot the model's predictions against the actual `female_unemployment`; recall the command is of the form

    ggplot(dframe, aes(x = pred, y = outcome)) + 
          geom_point() +  
          geom_abline()

Then you will calculate the residuals:

    residuals <- actual outcome - predicted outcome

and plot predictions against residuals. The residual graph will take a slightly different form: you compare the residuals to the horizonal line $x=0$ (using `geom_hline()`) rather than to the line $x=y$. The command will be provided.

```{r}
# unemployment is in the workspace
summary(unemployment)

# unemployment_model is in the workspace
summary(unemployment_model)

# Make predictions from the model
unemployment$predictions <- predict(unemployment_model)

# Fill in the blanks to plot predictions (on x-axis) versus the female_unemployment rates
ggplot(unemployment, aes(x = predictions, y = female_unemployment)) + 
  geom_point() + 
  geom_abline()

# Calculate residuals
unemployment$residuals <- unemployment$female_unemployment - unemployment$predictions

# Fill in the blanks to plot predictions (on x-axis) versus the residuals
ggplot(unemployment, aes(x = predictions, y = residuals)) + 
  geom_pointrange(aes(ymin = 0, ymax = residuals)) + 
  geom_hline(yintercept = 0, linetype = 3) + 
  ggtitle("residuals vs. linear model prediction")
```
